Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-08-22 Manuscript/manuscript.tex
Add preliminary intro

\todo{SAMULI: I can write preliminary version of the introduction asap.}

>>>>

Lipids with negatively charged headgroups, like phophatidylserine
play important role in biomembranes. Signaling domains interact with
anionic lipid membranes due to electrostatic and specific interactions
with negatively charged lipids \cite{??}.
Anionic lipids and their interactions with ions play also role in membrane
fusion \cite{??}.
These interactions depend on
chemical details of lipid headgroups and binding of counter and co-ions
to anionic membranes.

Various interaction schemes have been proposed for the negatively charged
lipids with ions and other lipids. Some studies suggest that the
binding constant to negatively charged lipids is similar to zwitterionic
and the binding affinity is increased only due to the increased cation
concentration in the vicinity of the membrane \cite{??}. On the other hand,
PS headgroups can form dehydrated complexes with calcium \cite{??} and ?? are
proposed to form complexes with ions \cite{??}. Different scenarios are
difficult to evaluate experimentally, especially with physiological
ion concentrations which are typically quite low.

Spectroscopic experiments give detailed information about the
interactions \cite{??}. The data is, however, often indirect and difficult
to interpret. Classical molecular dynamics (MD) simulations give
access to all the details, but the current force fields are not
sufficiently accurate to interpret the interactions of cationic
lipid headgroups with other lipids and ions \cite{NMRlipidsIV}.
Implicit inclusion of electronic polarizability using
electronic continuum correction (ECC) to lipid models
substantially improved the interactions between cations and
zwitterionic lipids \cite{melcr18}. Here, we extend the approach
to anionic PS lipids to more accurately describe its interactions with ions
and PC headgroups in mixed lipid bilayer. The results pave
the way for more realistic MD simulations of negatively charged
lipid bilayers to be used in wide range of applications.
